An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2014-04-11 mixedwindow.tex
Convert estimators and decorations to shorthand

\newcommand{\btrue}[1][]{\if#1*\hat\beta_{T+1}\else\beta_0\fi}

@@

Suppose for now that a researcher is interested in
predicting the target variable $y_{t+1}$ with a vector of regressors
$x_t$; also let $v_t$ be another random process that may contain information about
$y_{t+1}$ and suppose that
$(y_t, x_t, v_t)$ is stationary and weakly dependent
In addition,
let $\btrue = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudotrue
coefficient of the regression of $y_{t+1}$ on $x_t$ and define
$\varepsilon_{t+1} = y_{t+1} - x_t'\btrue$.  If this linear model is
correctly specified, then $\varepsilon_{t+1}$ is an \mds\ with respect
to the information set
\begin{equation*}
\mathcal{F}_t \equiv \sigma((x_t, v_t, y_t), (x_{t-1}, v_{t-1},
y_{t-1}),\dots),
\end{equation*}
and we can see immediately that
\begin{equation}
  \label{eq:4}
  \oclt{t} \varepsilon_{t+1} (v_t - x_t'\btrue)
\end{equation}
obeys an \mds\ \clt%
\footnote{This claim assumes that the asymptotic variance of the
  sample average is uniformly positive, a requirement that we will
  address in Section~\ref{sec:1b}.} %
and is asymptotically normal as $P \to \infty$, with $R$ an
arbitrary starting value%
\footnote{It will be clear momentarily why the
  summation begins at $R+1$ instead of $1$.} %
and $P = T - R$.%
\footnote{Section~\ref{sec:1b} discusses conditions under which the
  \mds\ condition holds. We will also present results that allow
  $\varepsilon_{t+1}$ to be serially correlated.} %
Straightforward algebra \citep{ClW:07} shows that
\begin{equation}
  \label{eq:5}
  \tfrac{1}{\sqrt{P}} \osum{t} \varepsilon_{t+1} (v_t -
  x_t'\btrue) = \tfrac{1}{2 \sqrt{P}} \osum{t} \Big[(y_{t+1} -
  x_t\btrue)^2 - (y_{t+1} - v_t)^2 + (x_t'\btrue - v_t)^2 \Big].
\end{equation}

\citet{ClW:06,ClW:07} base their \oos\ statistics on the RHS of
Equation~\eqref{eq:5}, but using a second forecast of $y_{t+1}$ as
$v_t$. (Call it $\hat{y}_{t+1}$.) They use a rolling window of length
$R$ to estimate $\hat{y}_{t+1}$;%
\footnote{Making $\hat{y}_{t+1}$ a function of $y_t, x_{t-1}, z_{t-1}
\dots, y_{t-R+1}, x_{t-R}$ and $z_{t-R}$, where $z_t$ is another weakly
dependent random process} %
$R$ is kept finite as $T \to \infty$, so
$\hat{y}_{t+1}$ inherits the weak dependence properties of the
variables used to estimate it. Using a finite window length $R$ avoids
the degeneracy that often arises in OOS test statistics (see
\citealp{ClM:01}, and \citealp{Mcc:07}), so the conditional variance
of the OOS average remains positive and the average obeys a \clt, an
approach introduced by \citet{GiW:06}.

\citet{ClW:06,ClW:07} develop a test of whether $\varepsilon_{t+1}$ is
an \mds. In the 2006 paper, Clark and West assume that the
coefficients $\btrue$ are zero under the null, making
$\varepsilon_{t+1}$ observed directly. This restriction is relaxed in
the 2007 paper where $\btrue$ is unknown and estimated with length-$R$
rolling window. Now the estimated linear model's prediction errors,
$\hat{\varepsilon}_{t+1}$, replace $\varepsilon_{t+1}$ in the \oos\
test statistic. Unfortunately, $\hat{\varepsilon}_{t+1}$ is not an
\mds\ even when $\varepsilon_{t+1}$ is, so the statistic is no longer
asymptotically mean-zero normal, even though this approximation
performs well in simulations.

This paper proposes using the same basic \oos\ statistic, 
but using a recursive window to estimate $\btrue$ and produce
$\hat{\varepsilon}_{t+1}$; so
\begin{equation}
  \label{eq:8}
  \hat{\beta}_t = \Big(\sum_{s=2}^{t} x_{t-1} x_{t-1}'\Big)^{-1}
  \sum_{s=2}^t x_{t-1} y_t.
\end{equation}
\citepos{Wes:96} Theorem 4.1 implies that
\begin{equation*}
  \oclt{t} \Big[(y_{t+1} -
  x_t\hat{\beta}_t)^2 - (y_{t+1} - v_t)^2 + (x_t'\hat{\beta}_t - v_t)^2 \Big]
\end{equation*}
is asymptotically normal with mean zero under the null for fairly
arbitrary processes $v_t$, as long as $v_t$ is weakly dependent and
the \oos\ statistic has uniformly positive variance.  Just as in
\citet{ClW:06,ClW:07}, these conditions are ensured if $v_t$ is
another forecast of $y_{t+1}$ based on a fixed-length rolling window.

@@

\begin{asmp}\label{a1}%
  The benchmark forecast $\hat{y}_{0,t+1}$, is estimated using \ols\
  with a recursive window: $\hat{y}_{0,t+1} = x_t'\hat{\beta}_t$ for
  some vector of predictors $x_t$ with $\hat{\beta}_t$ given by
  Equation~\eqref{eq:8}.  Also define $\btrue = (\E x_{t-1}
  x_{t-1}')^{-1} \E x_{t-1} y_t$ and assume that $\btrue$ does not
  depend on~$t$.

  The alternative forecast, $\hat{y}_{1t}$, is estimated using a
  rolling window of fixed length $R$ (which is less than $T$), so
  $\hat{y}_{1,t+1} = \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})$ where
  $\psi$ is a known function and $z_t$ is a sequence of predictors
  that may include $x_t$.
\end{asmp}

\begin{asmp}\label{a3}%
  The series $y_t$, $\hat{y}_{1t}$, and $x_t$ have uniformly bounded
  $2 r$ moments for some $r > 2$, and $\hat y_t y_t$ $\hat y_t
  x_{t-1}$, $y_t x_{t-1}$, and $x_{t-1}, x_{t-1}'$ are $L_2$-\ned\ of
  size $-\frac12$ on a strong mixing series of size $-\frac{r}{r-2}$
  for $r>2$ or a uniform mixing series of size $-\frac{r}{2r-2}$.
\end{asmp}

\begin{asmp}\label{a4}%
  Define \[f_t(\beta) = (y_{t+1} - x_t'\beta)^2 - (y_{t+1} -
  \hat{y}_{1,t+1})^2 + (x_t'\beta - \hat{y}_{1,t+1})^2,\] $f_t =
  f_t(\beta_0)$, $\hat f_t = f_t(\hat\beta_t)$, $\bar{f}(\beta) =
  \oavg{t} f_t(\beta)$, and $\bar f = \tfrac1P \sum_{t=R+1}^{T} \hat
  f_t$, with $P = T - R$; $\bar f(\btrue)$ has uniformly positive and
  finite long run variance.
\end{asmp}

@@

\begin{thm}\label{res:1}
  Suppose that we have two models $\hat{y}_{0t}$ and $\hat{y}_{1t}$ to
  forecast the variable $y_t$, and have observations for
  $t=1,\dots,T+1$. Suppose that Assumptions~\ref{a1} -- \ref{a4} hold.
  Under the null hypothesis that $y_t - \hat{y}_{0t}(\btrue)$ is a
  martingale difference sequence with respect to the filtration
  $\mathcal{F}_t = \sigma((y_t, z_{t}), (y_{t-1}, z_{t-1}),\dots)$,
  $\tfrac{\sqrt{P}}{\hat\sigma} \bar f \to^d N(0,1)$, where 
  \begin{align*}
    \hat{\sigma}^2 &= \hat{S}_{ff} + 2 (\hat{S}_{fg} + \hat{S}_{gg}), &
    \hat{S}_{ff} &= \oavg{t} (\hat f_t - \bar f)^2, \\
    \hat{S}_{fg} &= \oavg{t} (\hat f_t - \bar{f})(\hat g_t - \bar g)', &
    \hat{S}_{gg} &= \oavg{t} (\hat g_t - \bar g)(\hat g_t - \bar g)',
  \end{align*}
  $\bar{g} = \oavg{t}
  \hat g_t$, $\X' = [x_1,\dots,x_T]$,
  \begin{equation*}
    g_t(\beta) =
    \Big\{\tfrac{2}{P}\sum_{s=R}^T x_s (x_s'\beta - \hat{y}_{1,s+1}) \Big\}'
    \big(\tfrac1T \X'\X \big)^{-1} x_t(y_{t+1} - x_t'\beta),
  \end{equation*}
  and $\hat g_t = g_t(\hat\beta_t)$.
\end{thm}

@@

\begin{rem}
  The requirement that the asymptotic variance of $\bar f(\btrue)$ is
  uniformly positive is much less restrictive than in \cite{Wes:96}.
  As in \cite{GiW:06} and \citet{ClW:06,ClW:07}, the assumption only
  serves to rule out pathological cases---for example, letting both
  the benchmark and the alternative model be perfectly correlated white noise. In
  \citet{Wes:96}, this assumption is a restriction on the \dgp\ as
  well as the forecasting models, but in this paper it is a
  restriction only on the models.
\end{rem}

\begin{rem}
  The statistic we present tests the null hypothesis that the forecast
  errors from the population version of the benchmark model are a
  martingale difference sequence.  This hypothesis may not be
  appropriate, depending on the loss function or utility function of
  interest.  If one wants to test the less restrictive null hypothesis that
  $y_{t} - \hat{y}_{0t}$ is uncorrelated with $\hat{y}_{1t}$ but not
  necessarily an \mds, one can replace $\hat{S}_{ff}$, $\hat{S}_{fg}$
  and $\hat{S}_{gg}$ with their \hac\ counterparts.  
  Our statistic can also be modified to test implications of
  optimal forecasts under other loss functions
  \citep[see][]{PaT:07,PaT:07b}; the statistic should be expressed as
  a forecast encompassing test using the models' generalized forecast
  errors.%
\footnote{See \citet{HLN:98} and \citet[Section~4]{ClW:07}.} %
  Again, Lemma~\ref{res:a5} can cover these other applications.
\end{rem}

@@

Here, I conduct the same analysis, but using this paper's \mds\ test.
The benchmark model is the excess return's sample mean (as in the
original) and the alternative models are of the form
\[\text{excess return}_{t} = \alpha_{0} + \alpha_{1}\ 
\text{predictor}_{t-1} + \varepsilon_{t},\] where $\alpha_{0}$ and
$\alpha_{1}$ are estimated by \ols\ using a \windowlength-year window.
The predictors used are listed in the ``predictor'' column of
Table~\ref{tab:em1} \citep[see][for a detailed description of the
variables]{GoW:08}.  We also consider \citepos{CaT:08} proposed
correction to the models, that the forecasts be bounded below by zero
since negative forecasts are incredible, as well as two simple
combination forecasts, the mean and the median (over both the original
and the non-negative forecasts).  The data set is annual data
beginning in 1927 and ending in 2009, and the rolling window uses
\windowlength\ observations.%
\footnote{This statistical analysis was conducted in R \citep{R} and
  uses the MASS \citep[7.3-22]{VeR:02} package.} %

@@

However, we know that this is an extremely optimistic assessment of
the models' performance. We are conducting \nmod\ simultaneous
hypothesis tests, so it is likely that some will reject by chance. A
full treatment of this issue is beyond the scope of this paper,
however, it is straightforward to use Theorem~\ref{res:1} and
Lemma~\ref{lem:2} to derive an appropriate critical value as
in~\citet{Whi:00}. Since $\sqrt{P} \bar f \to^d N(0, \Sigma)$ under
the MDS null hypothesis, the continuous mapping theorem implies that
$\max_i \sqrt{P} \bar f_i/\hat\sigma_i \to^d \max_i W_i$, where $Z_i
\sim N(0, D^{-1/2} \Sigma D^{-1/2})$ and $D = \diag(\sigma_1, \dots,
\sigma_j)$. We can simulate from the $N(0, \hat D^{-1/2} \hat\Sigma
\hat D^{-1/2})$ distribution to generate a critical value for the
\emph{largest} individual test statistic under the null ---
\empiricalcriticalvalue, based on \empiricaldraws\ simulations. Using
this critical value, none of the predictors are siginificant at
\bootsize\%.%
\footnote{\citet{Han:05} makes the point that multiple one-sided
  comparisons can have poor power if irrelevant predictors are
  included in these tests and proposes a threshold for discarding very
  poor forecasts. His threshold is well below our worst performing
  model, so this issue is not a concern here. Moreover, I need to
  explain why it's not a concern for these statistics in general.} %

@@

\begin{proof}[Proof of Theorem \ref{res:1}]
  Replace $R$ with $\log(T)$ and $P$ with $T - \log(T)$ in the
  statistic; this substitution does not affect its asymptotic
  distribution.
  As in \citet{Wes:96} and \citet{WeM:98}, expand $\hat f_t$ around
  $\btrue$ to get
  \begin{align*}
    \sqrt{P} \big(\bar{f} - \bar{f}(\btrue)\big) &= \oclt{t}
    \big(f_t - \E f_t\big) +
    \E F_t B \oclt{t} H_t \\
    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t
  \end{align*}
  where (again, as in \citealp{Wes:96}) the $i$th element of $w_t$ is
  \begin{equation*}
    w_{it} = \tfrac12 (\hat\beta_t - \btrue)'
    \Big[\tfrac{\partial^2}{\partial \beta \partial\beta'}
    f_{it}(\tilde\beta_{it}) \Big]
    (\hat\beta_t - \btrue)
  \end{equation*}
  and each $\tilde\beta_{it}$ lies between $\hat\beta_t$ and
  $\btrue$; $\oclt{t} w_t = o_{p}(1)$ as in Theorem~\ref{res:3}.
  Then, as before,
  \begin{gather}
    \WesA \to^{p} 0 \label{eq:11} \\
    \WesB \to^{p} 0 \label{eq:12}\\
  \intertext{and}
    \WesC \to^{p} 0 \label{eq:13}
  \end{gather}
  from Lemma~\ref{res:a4}.  The formula of the asymptotic variance can
  be derived exactly as in \citet{Wes:96} and \citet{WeM:98}.

  Note that \[f_t(\btrue)= 2 (y_{t+1} -
  x_t'\btrue)(\hat{y}_{1,t+1} - x_t'\btrue) \quad \text{a.s.},\] as
  in \citet{ClW:07}, which is an \mds, so we do not need to use a
  \hac\ estimator of the variance under the null.  Also observe that
  \[F_t(\beta) = 2 x_t(x_t'\beta - \hat y_{1,t+1}) + 2 x_t(x_t'\beta -
  y_{t+1})\] and the second term is an \mds\ under the null,
  explaining the particular form of $g_t(\beta)$.
\end{proof}

@@

\begin{lema}\label{res:a2}
  Suppose $a \in [0,\frac12)$ and the conditions of Theorem~\ref{res:3}
  hold.
  \begin{enumerate}
  \item $P^a \sup_t | H_{t} | \to^p 0$.
  \item $P^a \sup_t | \hat{\beta}_{t} - \beta_{0} | \to^{p} 0$.
  \item $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T (F_t - \E F_t) = O_{p}(1)$.
  \end{enumerate}
\end{lema}

\begin{proof}[Proof of Lemma~\ref{res:a2}]
  \begin{enumerate}
  \item The process $\tfrac{1}{\sqrt{T}} h_{s}$ satisfies
    \citepos[Theorem 3.1]{JoD:00b} functional \clt.  So
    \begin{equation}
      P^a \sup_t \Big| \tfrac1t \sum_{s=1}^t h_{s} \Big| =
      P^a \sup_{\gamma \in [0,1]} \Big| \tfrac{1}{\lfloor \gamma
        T\rfloor} \sum_{s=1}^{\lfloor \gamma T \rfloor} h_{s} \Big| \to^{p} 0
    \end{equation}
    with the convergence following from the continuous mapping
    theorem.
  \item We have
    \begin{equation}
      P^a \sup_t | \hat{\beta}_t - \btrue | = P^a \sup_t |\hat{B}_{t}
      H_{t}| \leq \sup_{t,u} \Big| [ \hat{B}_u - B]
      \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big| + \sup_{t} \Big|
      B \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big|
    \end{equation}
    and both terms converge to zero in (conditional) probability by
    the previous argument and by assumption.
  \item $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T (F_t - \E F_t)$ obeys
    \citepos{Jon:97} \clt, so the result is trivial.
  \end{enumerate}
\end{proof}

>>>>

\newcommand{\Bh}{\hat{B}}
\newcommand{\btrue}[1][]{\if#1*\hat\beta_{T+1}\else\beta_0\fi}
\newcommand{\bh}{\hat{\beta}}
\newcommand{\bt}{\tilde{\beta}}
\newcommand{\ep}{\varepsilon}
\newcommand{\eph}{\hat{\varepsilon}}
\newcommand{\Fh}{\hat{F}}
\newcommand{\Fs}{\mathcal{F}}
\newcommand{\fb}{\bar{f}}
\newcommand{\fh}{\hat{f}}
\newcommand{\gb}{\bar{g}}
\newcommand{\gh}{\hat{g}}
\newcommand{\Sh}{\hat{S}}
\newcommand{\Sigmah}{\hat\Sigma}
\newcommand{\sh}{\hat\sigma}
\newcommand{\yh}{\hat{y}}

@@

Suppose for now that a researcher is interested in
predicting the target variable $y_{t+1}$ with a vector of regressors
$x_t$; also let $v_t$ be another random process that may contain information about
$y_{t+1}$ and suppose that
$(y_t, x_t, v_t)$ is stationary and weakly dependent
In addition,
let $\btrue = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudotrue
coefficient of the regression of $y_{t+1}$ on $x_t$ and define
$\ep_{t+1} = y_{t+1} - x_t'\btrue$.  If this linear model is
correctly specified, then $\ep_{t+1}$ is an \mds\ with respect
to the information set
\begin{equation*}
\mathcal{F}_t \equiv \sigma((x_t, v_t, y_t), (x_{t-1}, v_{t-1},
y_{t-1}),\dots),
\end{equation*}
and we can see immediately that
\begin{equation}
  \label{eq:4}
  \oclt{t} \ep_{t+1} (v_t - x_t'\btrue)
\end{equation}
obeys an \mds\ \clt%
\footnote{This claim assumes that the asymptotic variance of the
  sample average is uniformly positive, a requirement that we will
  address in Section~\ref{sec:1b}.} %
and is asymptotically normal as $P \to \infty$, with $R$ an
arbitrary starting value%
\footnote{It will be clear momentarily why the
  summation begins at $R+1$ instead of $1$.} %
and $P = T - R$.%
\footnote{Section~\ref{sec:1b} discusses conditions under which the
  \mds\ condition holds. We will also present results that allow
  $\ep_{t+1}$ to be serially correlated.} %
Straightforward algebra \citep{ClW:07} shows that
\begin{equation}
  \label{eq:5}
  \tfrac{1}{\sqrt{P}} \osum{t} \ep_{t+1} (v_t -
  x_t'\btrue) = \tfrac{1}{2 \sqrt{P}} \osum{t} \Big[(y_{t+1} -
  x_t\btrue)^2 - (y_{t+1} - v_t)^2 + (x_t'\btrue - v_t)^2 \Big].
\end{equation}

\citet{ClW:06,ClW:07} base their \oos\ statistics on the RHS of
Equation~\eqref{eq:5}, but using a second forecast of $y_{t+1}$ as
$v_t$. (Call it $\yh_{t+1}$.) They use a rolling window of length
$R$ to estimate $\yh_{t+1}$;%
\footnote{Making $\yh_{t+1}$ a function of $y_t, x_{t-1}, z_{t-1}
\dots, y_{t-R+1}, x_{t-R}$ and $z_{t-R}$, where $z_t$ is another weakly
dependent random process} %
$R$ is kept finite as $T \to \infty$, so
$\yh_{t+1}$ inherits the weak dependence properties of the
variables used to estimate it. Using a finite window length $R$ avoids
the degeneracy that often arises in OOS test statistics (see
\citealp{ClM:01}, and \citealp{Mcc:07}), so the conditional variance
of the OOS average remains positive and the average obeys a \clt, an
approach introduced by \citet{GiW:06}.

\citet{ClW:06,ClW:07} develop a test of whether $\ep_{t+1}$ is
an \mds. In the 2006 paper, Clark and West assume that the
coefficients $\btrue$ are zero under the null, making
$\ep_{t+1}$ observed directly. This restriction is relaxed in
the 2007 paper where $\btrue$ is unknown and estimated with length-$R$
rolling window. Now the estimated linear model's prediction errors,
$\eph_{t+1}$, replace $\ep_{t+1}$ in the \oos\
test statistic. Unfortunately, $\eph_{t+1}$ is not an
\mds\ even when $\ep_{t+1}$ is, so the statistic is no longer
asymptotically mean-zero normal, even though this approximation
performs well in simulations.

This paper proposes using the same basic \oos\ statistic, 
but using a recursive window to estimate $\btrue$ and produce
$\eph_{t+1}$; so
\begin{equation}
  \label{eq:8}
  \bh_t = \Big(\sum_{s=2}^{t} x_{t-1} x_{t-1}'\Big)^{-1}
  \sum_{s=2}^t x_{t-1} y_t.
\end{equation}
\citepos{Wes:96} Theorem 4.1 implies that
\begin{equation*}
  \oclt{t} \Big[(y_{t+1} -
  x_t\bh_t)^2 - (y_{t+1} - v_t)^2 + (x_t'\bh_t - v_t)^2 \Big]
\end{equation*}
is asymptotically normal with mean zero under the null for fairly
arbitrary processes $v_t$, as long as $v_t$ is weakly dependent and
the \oos\ statistic has uniformly positive variance.  Just as in
\citet{ClW:06,ClW:07}, these conditions are ensured if $v_t$ is
another forecast of $y_{t+1}$ based on a fixed-length rolling window.

@@

\begin{asmp}\label{a1}%
  The benchmark forecast $\yh_{0,t+1}$, is estimated using \ols\
  with a recursive window: $\yh_{0,t+1} = x_t'\bh_t$ for
  some vector of predictors $x_t$ with $\bh_t$ given by
  Equation~\eqref{eq:8}.  Also define $\btrue = (\E x_{t-1}
  x_{t-1}')^{-1} \E x_{t-1} y_t$ and assume that $\btrue$ does not
  depend on~$t$.

  The alternative forecast, $\yh_{1t}$, is estimated using a
  rolling window of fixed length $R$ (which is less than $T$), so
  $\yh_{1,t+1} = \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})$ where
  $\psi$ is a known function and $z_t$ is a sequence of predictors
  that may include $x_t$.
\end{asmp}

\begin{asmp}\label{a3}%
  The series $y_t$, $\yh_{1t}$, and $x_t$ have uniformly bounded
  $2 r$ moments for some $r > 2$, and $\yh_t y_t$ $\yh_t
  x_{t-1}$, $y_t x_{t-1}$, and $x_{t-1}, x_{t-1}'$ are $L_2$-\ned\ of
  size $-\frac12$ on a strong mixing series of size $-\frac{r}{r-2}$
  for $r>2$ or a uniform mixing series of size $-\frac{r}{2r-2}$.
\end{asmp}

\begin{asmp}\label{a4}%
  Define \[f_t(\beta) = (y_{t+1} - x_t'\beta)^2 - (y_{t+1} -
  \yh_{1,t+1})^2 + (x_t'\beta - \yh_{1,t+1})^2,\] $f_t =
  f_t(\btrue)$, $\fh_t = f_t(\bh_t)$, $\fb(\beta) =
  \oavg{t} f_t(\beta)$, and $\fb = \tfrac1P \sum_{t=R+1}^{T} \fh_t$
  with $P = T - R$; $\fb(\btrue)$ has uniformly positive and
  finite long run variance.
\end{asmp}

@@

\begin{thm}\label{res:1}
  Suppose that we have two models $\yh_{0t}$ and $\yh_{1t}$ to
  forecast the variable $y_t$, and have observations for
  $t=1,\dots,T+1$. Suppose that Assumptions~\ref{a1} -- \ref{a4} hold.
  Under the null hypothesis that $y_t - \yh_{0t}(\btrue)$ is a
  martingale difference sequence with respect to the filtration
  $\mathcal{F}_t = \sigma((y_t, z_{t}), (y_{t-1}, z_{t-1}),\dots)$,
  $\tfrac{\sqrt{P}}{\sh} \fb \to^d N(0,1)$, where
  \begin{align*}
    \sh^2 &= \Sh_{ff} + 2 (\Sh_{fg} + \Sh_{gg}), &
    \Sh_{ff} &= \oavg{t} (\fh_t - \fb)^2, \\
    \Sh_{fg} &= \oavg{t} (\fh_t - \fb)(\gh_t - \gb)', &
    \Sh_{gg} &= \oavg{t} (\gh_t - \gb)(\gh_t - \gb)',
  \end{align*}
  $\gb = \oavg{t}
  \gh_t$, $\X' = [x_1,\dots,x_T]$,
  \begin{equation*}
    g_t(\beta) =
    \Big\{\tfrac{2}{P}\sum_{s=R}^T x_s (x_s'\beta - \yh_{1,s+1}) \Big\}'
    \big(\tfrac1T \X'\X \big)^{-1} x_t(y_{t+1} - x_t'\beta),
  \end{equation*}
  and $\gh_t = g_t(\bh_t)$.
\end{thm}

@@

\begin{rem}
  The requirement that the asymptotic variance of $\fb(\btrue)$ is
  uniformly positive is much less restrictive than in \cite{Wes:96}.
  As in \cite{GiW:06} and \citet{ClW:06,ClW:07}, the assumption only
  serves to rule out pathological cases---for example, letting both
  the benchmark and the alternative model be perfectly correlated white noise. In
  \citet{Wes:96}, this assumption is a restriction on the \dgp\ as
  well as the forecasting models, but in this paper it is a
  restriction only on the models.
\end{rem}

Define $\X' = [x_1,\dots,x_T]$

\begin{align*}
  \Fh &= \Big\{\tfrac{2}{P}\sum_{s=R}^T x_s (x_s'\beta - \yh_{1,s+1}) \Big\}' &
  \Bh &= \big(\tfrac1T \X'\X \big)^{-1}
\end{align*}

Define the variables
$g_t(\beta) = \Fh \Bh x_t(y_{t+1} - x_t'\beta)$,
$\gh_t = g_t(\bh_t)$, and $\gb = \oavg{t} \gh_t$.

\newcommand{\K}[1]{K(\tfrac{#1}{w})}

Define the general covariance estimator:
\begin{align*}
  \Sigmah_1 &= \Sh_{21} + \Sh_{22} + \Sh_{22}' + 2 \, \Sh_{23}, &
  \Sh_{11} &= \oavg{s,t} (\fh_t - \fb) (\fh_t - \fb)' \K{t-s}, \\
  \Sh_{12} &= \oavg{s,t} (\fh_t - \fb)(\gh_t - \gb)' \K{t-s}, &
  \Sh_{13} &= \oavg{s,t} (\gh_t - \gb)(\gh_t - \gb)'  \K{t-s}.
\end{align*}

Define the MDS covariance estimator:
\begin{align*}
  \Sigmah_2 &= \Sh_{21} + \Sh_{22} + \Sh_{22}' + 2 \, \Sh_{23}, &
  \Sh_{21} &= \oavg{t} (\fh_t - \fb) (\fh_t - \fb)', \\
  \Sh_{22} &= \oavg{t} (\fh_t - \fb)(\gh_t - \gb)', &
  \Sh_{23} &= \oavg{t} (\gh_t - \gb)(\gh_t - \gb)'.
\end{align*}

\begin{lem}\label{lem:2}
  Under the conditions of Thoerem~\ref{res:1}, $\Sigmah_1 \to^p
  \Sigma$. If, in addition, $y_t - x_t'\btrue$ is an MDS with respect
  to $\Fs_t$ then $\Sigmah_2 \to^p \Sigma$.
\end{lem}

\begin{rem}
  The statistic we present tests the null hypothesis that the forecast
  errors from the population version of the benchmark model are a
  martingale difference sequence.  This hypothesis may not be
  appropriate, depending on the loss function or utility function of
  interest.  If one wants to test the less restrictive null hypothesis that
  $y_{t} - \yh_{0t}$ is uncorrelated with $\yh_{1t}$ but not
  necessarily an \mds, one can replace $\Sh_{21}$, $\Sh_{22}$
  and $\Sh_{23}$ with their \hac\ counterparts.
  Our statistic can also be modified to test implications of
  optimal forecasts under other loss functions
  \citep[see][]{PaT:07,PaT:07b}; the statistic should be expressed as
  a forecast encompassing test using the models' generalized forecast
  errors.%
\footnote{See \citet{HLN:98} and \citet[Section~4]{ClW:07}.} %
  Again, Lemma~\ref{res:a5} can cover these other applications.
\end{rem}

@@

Here, I conduct the same analysis, but using this paper's \mds\ test.
The benchmark model is the excess return's sample mean (as in the
original) and the alternative models are of the form
\[\text{excess return}_{t} = \alpha_{0} + \alpha_{1}\ 
\text{predictor}_{t-1} + \ep_{t},\] where $\alpha_{0}$ and
$\alpha_{1}$ are estimated by \ols\ using a \windowlength-year window.
The predictors used are listed in the ``predictor'' column of
Table~\ref{tab:em1} \citep[see][for a detailed description of the
variables]{GoW:08}.  We also consider \citepos{CaT:08} proposed
correction to the models, that the forecasts be bounded below by zero
since negative forecasts are incredible, as well as two simple
combination forecasts, the mean and the median (over both the original
and the non-negative forecasts).  The data set is annual data
beginning in 1927 and ending in 2009, and the rolling window uses
\windowlength\ observations.%
\footnote{This statistical analysis was conducted in R \citep{R} and
  uses the MASS \citep[7.3-22]{VeR:02} package.} %

@@

However, we know that this is an extremely optimistic assessment of
the models' performance. We are conducting \nmod\ simultaneous
hypothesis tests, so it is likely that some will reject by chance. A
full treatment of this issue is beyond the scope of this paper,
however, it is straightforward to use Theorem~\ref{res:1} and
Lemma~\ref{lem:2} to derive an appropriate critical value as
in~\citet{Whi:00}. Since $\sqrt{P} \fb \to^d N(0, \Sigma)$ under
the MDS null hypothesis, the continuous mapping theorem implies that
$\max_i \sqrt{P} \fb_i/\sh_i \to^d \max_i W_i$, where $Z_i
\sim N(0, D^{-1/2} \Sigma D^{-1/2})$ and $D = \diag(\sigma_1, \dots,
\sigma_j)$. We can simulate from the $N(0, \hat D^{-1/2} \Sh
\hat D^{-1/2})$ distribution to generate a critical value for the
\emph{largest} individual test statistic under the null ---
\empiricalcriticalvalue, based on \empiricaldraws\ simulations. Using
this critical value, none of the predictors are siginificant at
\bootsize\%.%
\footnote{\citet{Han:05} makes the point that multiple one-sided
  comparisons can have poor power if irrelevant predictors are
  included in these tests and proposes a threshold for discarding very
  poor forecasts. His threshold is well below our worst performing
  model, so this issue is not a concern here. Moreover, I need to
  explain why it's not a concern for these statistics in general.} %

@@

\begin{proof}[Proof of Theorem \ref{res:1}]
  Replace $R$ with $\log(T)$ and $P$ with $T - \log(T)$ in the
  statistic; this substitution does not affect its asymptotic
  distribution.
  As in \citet{Wes:96} and \citet{WeM:98}, expand $\fh_t$ around
  $\btrue$ to get
  \begin{align*}
    \sqrt{P} \big(\fb - \fb(\btrue)\big) &= \oclt{t}
    \big(f_t - \E f_t\big) +
    \E F_t B \oclt{t} H_t \\
    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t
  \end{align*}
  where (again, as in \citealp{Wes:96}) the $i$th element of $w_t$ is
  \begin{equation*}
    w_{it} = \tfrac12 (\bh_t - \btrue)'
    \Big[\tfrac{\partial^2}{\partial \beta \partial\beta'}
    f_{it}(\bt_{it}) \Big]
    (\bh_t - \btrue)
  \end{equation*}
  and each $\bt_{it}$ lies between $\bh_t$ and
  $\btrue$; $\oclt{t} w_t = o_{p}(1)$ as in Theorem~\ref{res:3}.
  Then, as before,
  \begin{gather}
    \WesA \to^{p} 0 \label{eq:11} \\
    \WesB \to^{p} 0 \label{eq:12}\\
  \intertext{and}
    \WesC \to^{p} 0 \label{eq:13}
  \end{gather}
  from Lemma~\ref{res:a4}.  The formula of the asymptotic variance can
  be derived exactly as in \citet{Wes:96} and \citet{WeM:98}.

  Note that \[f_t(\btrue)= 2 (y_{t+1} -
  x_t'\btrue)(\yh_{1,t+1} - x_t'\btrue) \quad \text{a.s.},\] as
  in \citet{ClW:07}, which is an \mds, so we do not need to use a
  \hac\ estimator of the variance under the null.  Also observe that
  \[F_t(\beta) = 2 x_t(x_t'\beta - \yh_{1,t+1}) + 2 x_t(x_t'\beta -
  y_{t+1})\] and the second term is an \mds\ under the null,
  explaining the particular form of $g_t(\beta)$.
\end{proof}

@@

\begin{lema}\label{res:a2}
  Suppose $a \in [0,\frac12)$ and the conditions of Theorem~\ref{res:3}
  hold.
  \begin{enumerate}
  \item $P^a \sup_t | H_{t} | \to^p 0$.
  \item $P^a \sup_t | \bh_{t} - \btrue | \to^{p} 0$.
  \item $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T (F_t - \E F_t) = O_{p}(1)$.
  \end{enumerate}
\end{lema}

\begin{proof}[Proof of Lemma~\ref{res:a2}]
  \begin{enumerate}
  \item The process $\tfrac{1}{\sqrt{T}} h_{s}$ satisfies
    \citepos[Theorem 3.1]{JoD:00b} functional \clt.  So
    \begin{equation}
      P^a \sup_t \Big| \tfrac1t \sum_{s=1}^t h_{s} \Big| =
      P^a \sup_{\gamma \in [0,1]} \Big| \tfrac{1}{\lfloor \gamma
        T\rfloor} \sum_{s=1}^{\lfloor \gamma T \rfloor} h_{s} \Big| \to^{p} 0
    \end{equation}
    with the convergence following from the continuous mapping
    theorem.
  \item We have
    \begin{equation}
      P^a \sup_t | \bh_t - \btrue | = P^a \sup_t |\Bh_{t}
      H_{t}| \leq \sup_{t,u} \Big| [ \Bh_u - B]
      \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big| + \sup_{t} \Big|
      B \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big|
    \end{equation}
    and both terms converge to zero in (conditional) probability by
    the previous argument and by assumption.
  \item $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T (F_t - \E F_t)$ obeys
    \citepos{Jon:97} \clt, so the result is trivial.
  \end{enumerate}
\end{proof}
